Crossing Origins by Crossing Formats

### 2012-12-03 main.tex
tweaks

The scenario, illustrated in Figure~\ref{fig:scenario}, describe how the attack proceed, from the infiltration of the origin, to the compromise of the victim.
The victim in this scenario is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
The target is infiltrated by the attacker, manipulating the website to serve polyglot content. Vulnerable.com serves the polyglot content as the benign content type, harmless to the victim. 
At a certain point, while still authenticated to vulnerable.com, 
the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com}.
The attacker.com website embeds the polyglot content from vulnerable.com, but
coerces the browser to interpret it as the malicious content type. 
The capabilities of the malicious format determine the 
severity of the consequences of exploitation.

>>>>

The scenario, illustrated in Figure~\ref{fig:scenario}, describe how the attack proceed, from the infiltration of the origin, to the compromise of the victim.
The victim in this scenario is an authenticated user of a targeted vulnerable website, \emph{vulnerable.com}. 
The target is infiltrated by the attacker, manipulating the website to
serve polyglot content. 
The \emph{vulnerable.com} site serves the polyglot content as the benign content type, harmless to the victim. 
At a certain point, while still authenticated to \emph{vulnerable.com}, 
the victim unsuspectingly visits the attackers malicious website, \emph{attacker.com}.
The \emph{attacker.com} site embeds the polyglot content from \emph{vulnerable.com}, but
coerces the browser to interpret it as the malicious content type. 
The capabilities of the malicious format determine the 
severity of the consequences of exploitation.

To give more context to the scenario, \emph{vulnerable.com} can be a cloud storage service. 
The attacker infiltrates the target by uploading a polyglot to the service and embed it 
on \emph{attacker.com}. While authenticated to \emph{vulnerable.com}, the unsuspecting victim visits \emph{attacker.com}, the embedded 
polyglot is activated and extracts all the files stored in the victims account.
